% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

% \cvtag{Hard-working (18/24)}
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Experience}
\cvexperience{Software Engineer Intern}{May. 2021--Present}{Reston, VA}{ScienceLogic}
\begin{itemize}
    \item Maintain and implement BDD and unit tests, improve code coverage for the SL1 data collection backend application with Python and MySQL.
    \item Instrument data processing app with counters that can be logged in a periodic service summary report in the service logs.
    \item Work within a scrum team in the agile workflow. Participate in daily standup as well as weekly sprint planning \& retro.
\end{itemize}
\smallskip
\cvexperience{CS Ethics Tech Lead/Teaching Assistant}{Aug. 2019--May 2021}{}{}
\begin{itemize}
    \item Held weekly office hours; offered technical supports and environment configuration; assisted in \textit{Software Engineering}, \textit{Data Structure} courses in lab sessions.
    \item Participated in Mozilla Responsible Computer Science Challenge; assisted in course planning with CS ethics emphasis.
    \item Led student software engineer teams implementing department tools; mentored students in contributing to open source softwares such as Pandas and Zulip.
\end{itemize}
\smallskip
\cvexperience{Club Founder/President}{May 2019--May 2021}{Meadville, PA}{Electronic Music at Allegheny College}
\begin{itemize}
\item Founded the first music club on campus, dedicates to establishing inter-disciplinary art culture and providing platform for non-musicians to create music using Ableton, Max/Msp, Processing;
\item Springboarded the first electronic music event on campus with hundreds of students participating.
\end{itemize}
\smallskip
\cvexperience{Pianist | Stage Manager}{July 2019--Aug. 2019}{Los Angeles, CA}{Montecito International Music Festival}
\begin{itemize}
\item Performed in recitals and ensembles with world class musicians and students.
\item Arranged stage settings and lights in concerts with stage crews and musicians.
\end{itemize}
\smallskip
\cvexperience{Research Assistant}{Aug. 2018--May 2019}{}{}
\begin{itemize}
\item Collaborated with Dr. Sharon Wesoky and assisted in translating materials on Buddhist practitioners in China and Chinese feminism.
\end{itemize}
\smallskip

\cvsection{Projects}
\cvproject{Automated FastAPI-EC2-Streamlit Application}{Dec. 2020}{}
\begin{itemize}
\item Led team of 3 implemented an automated deployment web application that performs stock price and twitter sentiment relation analysis.
\item Automated EC2 and API deployment with boto, FastAPI, and Docker using Python and Shell script; created customized visualization on Streamlit.
\end{itemize}
\smallskip
\cvproject{Tada: Automated Order-of-growth Analysis}{May 2020}{}
\begin{itemize}
\item Built and deployed Python CLI application that ascertains worst-case time complexity for any arbitrary Python function, presented at Code PaLOUsa.
\item Implemented automated random data generation with JSONSchema for rigorous-fashion experiment. Increased test coverage to 98\%.
\item Designed and maintain documentation website with MkDocs; Enable automated release through CI/CD with Github Action.
\end{itemize}
\smallskip
\cvproject{Text Mining with Visualization}{Apr. 2020}{}
\begin{itemize}
\item Built Python visualized text mining application with CLI and web interface, presented at PyCon 2020 poster session.
\item Designed and enabled automated deployment of a Gateway-Lambda-DynamoDB framework, with data collection through Gradle in Github.
\item Implemented topic modeling, similarity analysis with features including sentiment analysis and named-entity recognition with SpaCy and Gensim.
%\smallskip
\end{itemize}
\smallskip
% \cvproject{Santa: Automated Testing Application}{May 2019}{}
% \begin{itemize}
% \item Led a team of 5 developing automated testing python plugin for course project.
% \item Designed and built a Pytest plugin framework that integrates automated type inferring and test data generation with MonkeyType and Hypothesis.
% \end{itemize}
\smallskip
% \cvproject{Java Framework for Alternating Variable Method}{Aug. 2018}{}
% \begin{itemize}
% \item Enabled Travis CI; developed usage documentation; increased test coverage.
% \item Researched in heuristic algorithms in search-based optimization problems.
% \end{itemize}

%% \cvsection{PUBLICATIONS}
%% \smallskip
%% \begin{itemize}
%% \item R. Jain, H. Tulsani, A. Bansal, "A two- tier steganographic model based on (2,2)VCS %% and integer wavelet transform", in Preceding of The 5th International Conference on %% Computing for Sustainable Global Development organized by IEEE, pp. 4731-4734, (2018).
%%\smallskip
%%\end{itemize}
